\documentclass[11pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{caption} % for table captions
\usepackage{amsmath} % for multi-line equations and piecewises
\DeclareMathOperator{\sign}{sign}
\usepackage{graphicx}
\usepackage{relsize}
%\usepackage{textcomp}
\usepackage{xspace}
\usepackage{verbatim} % for block comments
%\usepackage{subfig} % for subfigures
\usepackage{enumitem} % for a) b) c) lists
\newcommand{\Cyclus}{\textsc{Cyclus}\xspace}%
\newcommand{\Cycamore}{\textsc{Cycamore}\xspace}%
\usepackage{tabularx}
\usepackage{color}
\usepackage[acronym,toc]{glossaries}
\include{acros}
\definecolor{bg}{rgb}{0.95,0.95,0.95}
\newcolumntype{b}{X}
\newcolumntype{f}{>{\hsize=.15\hsize}X}
\newcolumntype{s}{>{\hsize=.5\hsize}X}
\newcolumntype{m}{>{\hsize=.75\hsize}X}
\newcolumntype{r}{>{\hsize=1.1\hsize}X}
\usepackage{titling}
\usepackage[hang,flushmargin]{footmisc}
\renewcommand*\footnoterule{}
\usepackage[newfloat]{minted}
\newenvironment{code}{\captionsetup{type=listing}}{}
\SetupFloatingEnvironment{listing}{name=Code}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}

\bibliographystyle{abbrv}
\usepackage{tikz}


\usetikzlibrary{shapes.geometric,arrows}
\tikzstyle{process} = [rectangle, rounded corners, minimum width=1cm, minimum height=1cm,text centered, draw=black, fill=blue!30]
\tikzstyle{arrow} = [thick,->,>=stealth]


\graphicspath{{images/}}
\title{Numerical Experiments for Verifying Demand Driven Deployment Algorithms 
        \\ \vspace{0.5em} Non-Optimizing Algorithm}
\author{Jin Whan Bae, Gwendolyn Chee, Kathryn Huff}


\begin{document}
	\maketitle
	\hrule

\section{Project Objective}
The Demand-Driven Cycamore Archetype project (NEUP-FY16-10512) aims to develop \Cycamore demand-driven deployment capabilities. The developed algorithm, in the form of \Cyclus \texttt{Institution}
agent, deploys \texttt{Facilities} to meet the front-end and back-end demands of the 
fuel cycle.

\section{Motivation}
For many fuel cycle simulations, it is currently up to the user to define
a deploy scheme, or facility parameters, to make sure that there's no gap
in the supply chain. Or, the same goal is achieved by setting the
\texttt{facility} capacity to infinity, which does not reflect real-world
conditions. 

\section{Method}
The project objective is met by developing three types of predictive algorithms: non-optimizing, deterministic-optimizing and stochastic-optimizing. Each algorithm aims to improve on the previous 
to provide more accurate results. 

These prediction algorithms are being developed by the University of South Carolina. Numerical experiments will be designed for both the once through nuclear fuel cycle and advanced fuel cycles. 

This report focuses on the non-optimizing algorithm. 
It lists capability requirements of the non-optimizing case of the new \Cyclus \texttt{institute}
for demand-driven deployment of fuel cycle facilities. 
It also discusses the tests to check correct implementation of the capabilities,
with a sample fuel cycle with well-defined facility parameters.

\section{Archetype Requirements}
Subsections \ref{subsection-user} to \ref{subsection-rate} state the requirements that apply to all three predictive algorithms. Expectations for the non-optimizing algorithm are different than for the deterministic-optimizing and stochastic-optimizing. Therefore, in subsections \ref{subesction-deploy} to \ref{subsection-volatile}, the requirements unique to the non-optimizing algorithm are specified. 

\subsection{User Configuration}
\label{subsection-user}
The archetype should allow the user to define the following parameters: 
\begin{enumerate}
	\item A commodity whose demand drives deployment
	\item Initial amount of that demand
	\item Rate of growth or decline of that demand
	\item The facilities in the simulation able to meet that demand
	\item Algorithm type: non-optimizing, deterministic optimizing or stochastic optimizing
\end{enumerate}

\subsection{Create a supply chain}
\label{subsection-supplychain}
The archetype should be able to access the user defined parameter for the facilities in the simulation and evaluate if the commodities supplied by these facilities produce an appropriate supply chain to meet the demand of the commodity whose demand drives deployment. If not, the archetype should inform the user by throwing an error.  

\subsection{High-level Functionality}
A high-level example of how the archetype should work is: if the user chooses a positive demand growth equation for power and facilities present in the simulation to be reactor and fuel facilities. The power demand will trigger reactor deployment which causes an increase in the demand of fuel, which triggers fuel facility deployment.

\subsection{Growth or Decline Rate}
\label{subsection-rate}
The archetype should give the user options for different types of growth or decline rate curves. Possible examples could be linear, exponential or piece-wise. 

\subsection{Facility Deployment and Decommissioning }
\label{subesction-deploy}
 The non-optimizing algorithm's deployment and decommissioning capabilities should be based on previous demand and supply values. At each time step, the algorithm should evaluate the demand for each commodity against its corresponding supply. If there is a shortage or surplus, the algorithm should deploy new facilities or decommission existing facilities. With an exception to the case where decommissioning of a facility due to surplus of a commodity will result in the shortage of the commodity. This is a reflection of reality, since it is acceptable to have some surplus in storage as opposed to shortage of a commodity that could result in non-maximum capacity of a nuclear reactor. 
 
 \subsection{Dealing with volatility}
 \label{subsection-volatile}
A comprehensive fuel cycle simulator must have predictive capabilities which 
can deploy fuel cycle support facilities intelligently even in the face of 
volatile dynamics. In the situation where the commodity whose demand 
drives deployment changes in a volatile manner, the archetype should
be able to recognize this and not deploy and decommission the same facility across
short time periods due to volatile changes in commodity demand. 

\section{Simulation parameter for Test Scenarios}
Simple parameters are given to fuel cycle facilities for the numerical testing of 
the algorithm.  Only \texttt{source} and \texttt{reactor} facilities are used in the test scenarios. 

Table \ref{tab:testscenario} provides basic parameters for each test scenario. Table \ref{tab:reactor} provides the parameters for the \texttt{source}, \texttt{reactors} and \texttt{sink} in the test scenarios.

\begin{table}[H]
	\centering
	\caption {Basic Test Parameters}
	\label{tab:testscenario}
	\begin{tabular}{|l|l|l|}
		\hline
		\textbf{Test Scenario Parameters} & \textbf{Value} & \textbf{Units} \\
		\hline
		Duration & 15 & timesteps \\
		Timestep & 1 & month \\
		Start Month & 1 & month \\
		Start Year & 2000 & year \\
		\hline
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
    \caption {Source, Reactor and Sink Parameters}
	\label{tab:reactor}
	\begin{tabular}{|l|l|l|}
\hline
\textbf{Source Parameters} & \textbf{Value} & \textbf{Units} \\
\hline
Throughput & 1 & kg \\
Output Commodity & fuel & kg\\
\hline
\textbf{Reactor Parameters} & \textbf{Value} & \textbf{Units} \\
\hline
Cycle Time & 1 & timesteps \\
Refuel Time & 0 & timesteps \\
Lifetime & 1 & timesteps \\
Power Capacity & 1& MWe \\
Assembly Size & 1 & kg \\
\# assemblies per core & 1 & \\
\# assemblies per batch & 1 & \\
Input Commodity & fuel & kg\\
Output Commodity & power & MW\\
\hline
\textbf{Sink Parameters} & \textbf{Value} & \textbf{Units} \\
Throughput & 1 & kg \\
Input Commodity & spent uox & kg\\
\hline
	\end{tabular}
\end{table}

\pagebreak

\section{Numerical Tests for the Non-optimizing prediction method}
The non-optimizing prediction method is tested by comparing its output for various scenarios against their analytical solutions . In this section, the tests that must be met is described based on the parameters defined in table \ref{tab:testscenario} and \ref{tab:reactor} and analytical solution of a defined simple scenario. Unit test examples are included in Appendix B.

The tests are in forms of \texttt{[alphabet]-[traj]-[num]}. \texttt{Alphabet} refers to the supply chain of the test scenario,
\texttt{traj} the demand change in time, and \texttt{num} for tests with the same \texttt{alphabet} and \texttt{traj}.
\begin{itemize}
	\item \textbf{A} - source $\rightarrow$ \texttt{End Demand Commodity}
	\item \textbf{B} - source $\rightarrow$ reactor $\rightarrow$ \texttt{End Demand Commodity}
\end{itemize}

Note that for test C, the \texttt{End Demand Commodity} is power generated from the reactor. The C-tests additionally
check if the sink is deployed to meet spent fuel disposal demand.

The prediction algorithm for the non-optimizing method has three user-defined input parameters. The aim of the various test scenarios are to check if the non-optimizing method archetype will deploy or decommission facilities correctly when there is a variation in the combination of the three input parameters.  The input parameters are: 
\begin{enumerate}
	\item Initial demand value  
	\item Number of initial facilities (initial supply)
	\item Growth rate of initial demand
\end{enumerate}

The growth in demand is governed by the Equation \ref{eq:growth}. 

\begin{align}
\label{eq:growth}
D_f(timestep) &= D_i(1+g)^{(\frac{timestep}{12})}
\end{align}
Where $D_f$ is demand of resource at specific time step, $D_i$ is initial demand and g is growth rate. 

\texttt{Source} and \texttt{reactor} facilities are used in the test scenarios. Test scenarios A1 to A4 and B1 to B2 only have a \texttt{source} facility and test scenarios A5 to A7 have both \texttt{source} and \texttt{reactor} facilities. For each test scenario, there is one table that states the test scenario's input parameters and another table that states the exact analytical solution. The analytical solution table does not include deployment of the initial facility that is stated in the first table.

Additionally, we created base tests for each A-type test scenario that passes when the supply meets the demand within a given facility number tolerance. In other words, when the supply exceeds the demand by the specified tolerance quantity, the test still passes. For this report, the tolerance is set to one facility. For example in test A-1, the expected total number facilities deployed is 1, and since the facility over-prediction tolerance is 1, the acceptable range of total number of facilities $(x)$ deployed in the entire test scenario is $1<x<2$. If the total number of facilities deployed is within this range, the base case test will pass.  

\subsection{Test A-const-1}
In test A-const-1, only a \texttt{source} facility is present in the test scenario. Table \ref{tab:test-A-const-1} shows the input parameters of the source facility in the test scenario. Table \ref{tab:test-A-const-1ana} shows the expected analytical solution based on the test scenario. Table \ref{tab:test-A-const-1base} shows the accepted range of total number of facilities deployed over the test scenario which will pass the base test, which factors in the facility over-prediction tolerance of 1. 
\begin{table}[H]
	\centering
	\caption{Test A-const-1 Scenario Input Parameters }
	\label{tab:test-A-const-1}
	\begin{tabular}{|l|l|l|}
		\hline
		\textbf{Source Parameter} & \textbf{Value} & \textbf{Units} \\
		\hline
		Initial demand & 1 & kg \\
		Initial facilities & 0 & \#\\
		Growth Rate & 0 & \\
\hline
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
	\caption{Test A-const-1 Analytical Solution}
	\label{tab:test-A-const-1ana}
	\begin{tabular}{|l|l|}
		\hline
		\textbf{Time Step} & \textbf{\shortstack{No. of Source \\Facilities Deployed}}\\
		\hline
		1 & 1\\
		2 to 15& 0 \\
		\hline
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
	\caption{Test A-const-1 Base Test Acceptance}
	\label{tab:test-A-const-1base}
	\begin{tabular}{|P{6.5cm}|}
		\hline
		\textbf{\shortstack{Acceptable total No. of Source \\Facilities Deployed + tolerance}}\\
		\hline
		1 $<$ x $<$ 2 \\
		\hline
	\end{tabular}
\end{table}

\subsection{Test A-const-2}
In test A-const-2, only a \texttt{source} facility is present in the test scenario. Table \ref{tab:test-A-const-2} shows the input parameters of the source facility in the test scenario. Table \ref{tab:test-A-const-2ana} shows the expected analytical solution based on the test scenario.Table \ref{tab:test-A-const-2base} shows the accepted range of total number of facilities deployed over the test scenario which will pass the base test, which factors in the facility over-prediction tolerance of 1. 

\begin{table}[H]
	\centering
	\caption{Test A-const-2 Scenario Input Parameters }
	\label{tab:test-A-const-2}
	\begin{tabular}{|l|l|l|}
		\hline
		\textbf{Source Parameter} & \textbf{Value} & \textbf{Units} \\
		\hline
		Initial demand & 2 & kg \\
		Initial facilities & 1 & \#\\
		Growth Rate & 0 & \\
		\hline
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
	\caption{Test A-const-2 Analytical Solution}
	\label{tab:test-A-const-2ana}
	\begin{tabular}{|l|l|}
		\hline
		\textbf{Time Step} & \textbf{\shortstack{No. of Source \\Facilities Deployed}}\\
		\hline
		1 & 1\\
		2 to 15& 0 \\
		\hline
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
	\caption{Test A-const-2 Base Test Acceptance}
	\label{tab:test-A-const-2base}
	\begin{tabular}{|P{6.5cm}|}
		\hline
		\textbf{\shortstack{Acceptable total No. of Source \\Facilities Deployed + tolerance}}\\
		\hline
		2 $<$ x $<$ 3 \\
		\hline
	\end{tabular}
\end{table}

\subsection{Test A-grow-1}
In test A-grow-1, only a \texttt{source} facility is present in the test scenario. Table \ref{tab:test-A-grow-1} shows the input parameters of the source facility in the test scenario. Table \ref{tab:test-A-grow-1ana} shows the expected analytical solution based on the test scenario. Table \ref{tab:test-A-grow-1base} shows the accepted range of total number of facilities deployed over the test scenario which will pass the base test, which factors in the facility over-prediction tolerance of 1. 

\begin{table}[H]
	\centering
	\caption{Test A-grow-1 Scenario Input Parameters}
	\label{tab:test-A-grow-1}
	\begin{tabular}{|l|l|l|}
		\hline
		\textbf{Source Parameter} & \textbf{Value} & \textbf{Units} \\
		\hline
		Initial demand & 1 & kg \\
		Initial facilities & 0 & \#\\
		Growth Rate & 1 &  \\
		\hline
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
	\caption{Test A-grow-1 Analytical Solution}
	\label{tab:test-A-grow-1ana}
	\begin{tabular}{|l|l|}
		\hline
		\textbf{Time Step} & \textbf{\shortstack{No. of Source \\Facilities Deployed}}\\
		\hline
		1 & 2\\
		2 to 12 & 0 \\
		13 & 1 \\
		14 to 15 & 0 \\
		\hline
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
	\caption{Test A-grow-1 Base Test Acceptance}
	\label{tab:test-A-grow-1base}
	\begin{tabular}{|P{6.5cm}|}
		\hline
		\textbf{\shortstack{Acceptable total No. of Source \\Facilities Deployed + tolerance}}\\
		\hline
		3 $<$ x $<$ 4 \\
		\hline
	\end{tabular}
\end{table}

\subsection{Test A-grow-2}
In test A-grow-2, only a \texttt{source} facility is present in the test scenario. Table \ref{tab:test-A-grow-2} shows the input parameters of the source facility in the test scenario. Table \ref{tab:test-A-grow-2ana} shows the expected analytical solution based on the test scenario. Table \ref{tab:test-A-grow-2base} shows the accepted range of total number of facilities deployed over the test scenario which will pass the base test, which factors in the facility over-prediction tolerance of 1. 

\begin{table}[H]
	\centering
	\caption{Test A-grow-2 Scenario Input Parameters }
	\label{tab:test-A-grow-2}
	\begin{tabular}{|l|l|l|}
		\hline
		\textbf{Source Parameter} & \textbf{Value} & \textbf{Units} \\
		\hline
		Initial demand & 1 & kg \\
		Initial facilities & 1 & \#\\
		Growth Rate & 1 &  \\
		\hline
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
	\caption{Test A-grow-2 Analytical Solution}
	\label{tab:test-A-grow-2ana}
	\begin{tabular}{|l|l|}
		\hline
		\textbf{Time Step} & \textbf{\shortstack{No. of Source \\Facilities Deployed}}\\
		\hline
		1 & 1\\
		2 to 12 & 0 \\
		13 & 1 \\
		14 to 15 & 0 \\
		\hline
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
	\caption{Test A-grow-2 Base Test Acceptance}
	\label{tab:test-A-grow-2base}
	\begin{tabular}{|P{6.5cm}|}
		\hline
		\textbf{\shortstack{Acceptable total No. of Source \\Facilities Deployed + tolerance}}\\
		\hline
		3 $<$ x $<$ 4 \\
		\hline
	\end{tabular}
\end{table}

\subsection{Test B-const-1}
In test B-const-1, both a \texttt{source} and \texttt{reactor} facility is present in the test scenario. Table \ref{tab:test-B-const-1} shows the input parameters of the source facility in the test scenario. Table \ref{tab:test-B-const-1ana} shows the expected analytical solution based on the test scenario. Table \ref{tab:test-B-const-1base} shows the accepted range of total number of facilities deployed over the test scenario which will pass the base test, which factors in the facility over-prediction tolerance of 1. 

\begin{table}[H]
	\centering
	\caption{Test B-const-1 Scenario Input Parameters}
	\label{tab:test-B-const-1}
	\begin{tabular}{|l|l|l|}
		\hline
		\textbf{Source Parameter} & \textbf{Value} & \textbf{Units} \\
		\hline
		Initial demand & 1 & kg \\
		Initial facilities & 0 & \#\\
		Growth Rate & 0 &  \\
		\hline
		\textbf{Reactor Parameter} & \textbf{Value} & \textbf{Units} \\
		\hline
		Initial demand & 1 & MW \\
		Initial facilities & 0 & \#\\
		Growth Rate & 0 &  \\
		\hline
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
	\caption{Test B-const-1 Analytical Solution}
	\label{tab:test-B-const-1ana}
	\begin{tabular}{|l|l|l|}
		\hline
		\textbf{Time Step} & \textbf{\shortstack{No. of Source \\Facilities Deployed}} & \textbf{\shortstack{No. of Reactor \\Facilities Deployed}}\\
		\hline
		1 & 1 & 1\\
		2 to 15 & 0 & 0\\
		\hline
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
	\caption{Test B-const-1 Base Test Acceptance}
	\label{tab:test-B-const-1base}
	\begin{tabular}{|P{6.5cm}|P{6.5cm}|}
		\hline
		\textbf{\shortstack{Acceptable total No. of Source \\Facilities Deployed + tolerance}} &\textbf{\shortstack{Acceptable total No. of Reactor \\Facilities Deployed + tolerance}}\\
		\hline
		1 $<$ x $<$ 2 & 1 $<$ x $<$ 2\\
		\hline
	\end{tabular}
\end{table}

\subsection{Test B-const-2}
In test B-const-2, both a \texttt{source} and \texttt{reactor} facility is present in the test scenario. Table \ref{tab:test-B-const-2} shows the input parameters of the source facility in the test scenario. Table \ref{tab:test-B-const-2ana} shows the expected analytical solution based on the test scenario. Table \ref{tab:test-B-const-2base} shows the accepted range of total number of facilities deployed over the test scenario which will pass the base test, which factors in the facility over-prediction tolerance of 1. 

\begin{table}[H]
	\centering
	\caption{Test B-const-2 Scenario Input Parameters }
	\label{tab:test-B-const-2}
	\begin{tabular}{|l|l|l|}
		\hline
		\textbf{Source Parameter} & \textbf{Value} & \textbf{Units} \\
		\hline
		Initial demand & 1 & kg \\
		Initial facilities & 1 & \#\\
		Growth Rate & 0 &  \\
		\hline
		\textbf{Reactor Parameter} & \textbf{Value} & \textbf{Units} \\
		\hline
		Initial demand & 1 & MW \\
		Initial facilities & 1 & \#\\
		Growth Rate & 0 &  \\
		\hline
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
	\caption{Test B-const-2 Analytical Solution}
	\label{tab:test-B-const-2ana}
	\begin{tabular}{|l|l|l|}
		\hline
		\textbf{Time Step} & \textbf{\shortstack{No. of Source \\Facilities Deployed}} & \textbf{\shortstack{No. of Reactor \\Facilities Deployed}}\\
		\hline
		1 & 1 & 1\\
		2 to 15 & 0 & 0\\
		\hline
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
	\caption{Test B-const-2 Base Test Acceptance}
	\label{tab:test-B-const-2base}
	\begin{tabular}{|P{6.5cm}|P{6.5cm}|}
		\hline
		\textbf{\shortstack{Acceptable total No. of Source \\Facilities Deployed + tolerance}} &\textbf{\shortstack{Acceptable total No. of Reactor \\Facilities Deployed + tolerance}}\\
		\hline
		1 $<$ x $<$ 2 & 1 $<$ x $<$ 2\\
		\hline
	\end{tabular}
\end{table}

\subsection{Test B-grow-1}
In test B-grow-1, both a \texttt{source} and \texttt{reactor} facility is present in the test scenario. Table \ref{tab:test-B-grow-1} shows the input parameters of the source facility in the test scenario. Table \ref{tab:test-B-grow-1ana} shows the expected analytical solution based on the test scenario. Table \ref{tab:test-B-grow-1base} shows the accepted range of total number of facilities deployed over the test scenario which will pass the base test, which factors in the facility over-prediction tolerance of 1. 


\begin{table}[H]
	\centering
	\caption{Test B-grow-1 Scenario Input Parameters }
	\label{tab:test-B-grow-1}
	\begin{tabular}{|l|l|l|}
		\hline
		\textbf{Source Parameter} & \textbf{Value} & \textbf{Units} \\
		\hline
		Initial demand & 1 & kg \\
		Initial facilities & 0 & \#\\
		Growth Rate & 1 &  \\
		\hline
		\textbf{Reactor Parameter} & \textbf{Value} & \textbf{Units} \\
		\hline
		Initial demand & 1 & MW \\
		Initial facilities & 0 & \#\\
		Growth Rate & 1 &  \\
		\hline
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
	\caption{Test B-grow-1 Analytical Solution}
	\label{tab:testB-grow-1ana}
	\begin{tabular}{|l|l|l|}
		\hline
		\textbf{Time Step} & \textbf{\shortstack{No. of Source \\Facilities Deployed}} & \textbf{\shortstack{No. of Reactor \\Facilities Deployed}}\\
		\hline
		1 & 2 & 2\\
		2 to 12 & 0 & 0\\
		13 & 1 & 1\\
		14 to 15 & 0 & 0\\
		\hline
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
	\caption{Test B-grow-1 Base Test Acceptance}
	\label{tab:test-B-grow-1base}
	\begin{tabular}{|P{6.5cm}|P{6.5cm}|}
		\hline
		\textbf{\shortstack{Acceptable total No. of Source \\Facilities Deployed + tolerance}} &\textbf{\shortstack{Acceptable total No. of Reactor \\Facilities Deployed + tolerance}}\\
		\hline
		3 $<$ x $<$ 4 & 3 $<$ x $<$ 4\\
		\hline
	\end{tabular}
\end{table}

\subsection{Test A-const-3}
In test A-const-3, only a \texttt{source} facility is present in the test scenario. Table \ref{tab:test-A-const-3} shows the input parameters of the source facility in the test scenario. Table \ref{tab:test-A-const-3ana} shows the expected analytical solution based on the test scenario. 

\begin{table}[H]
	\centering
	\caption{Test A-const-3 Scenario Input Parameters }
	\label{tab:test-A-const-3}
	\begin{tabular}{|l|l|l|}
		\hline
		\textbf{Source Parameter} & \textbf{Value} & \textbf{Units} \\
		\hline
		Initial demand & 0 & kg \\
		Initial facilities & 1 & \#\\
		Growth Rate & 0 &  \\
		\hline
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
	\caption{Test A-const-3 Analytical Solution}
	\label{tab:test-A-const-3ana}
	\begin{tabular}{|l|l|l|}
		\hline
		\textbf{Time Step} & \textbf{\shortstack{No. of Source \\Facilities Deployed}}& \textbf{\shortstack{No. of Source \\Facilities Decomissioned}}\\
		\hline
		1 & 1 & 0\\
		2 & 0 & 1\\
		3 to 15 & 0 & 0\\
		\hline
	\end{tabular}
\end{table}

\subsection{Test A-decl-1}
In test A-decl-1, only a \texttt{source} facility is present in the test scenario. Table \ref{tab:test-A-decl-1} shows the input parameters of the source facility in the test scenario. Table \ref{tab:test-A-decl-1ana} shows the expected analytical solution based on the test scenario.

\begin{table}[H]
	\centering
	\caption{Test A-decl-1 Scenario Input Parameters }
	\label{tab:test-A-decl-1}
	\begin{tabular}{|l|l|l|}
		\hline
		\textbf{Source Parameter} & \textbf{Value} & \textbf{Units} \\
		\hline
		Initial demand & 1 & kg \\
		Initial facilities & 1 & \#\\
		Growth Rate & -1 &  \\
		\hline
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
	\caption{Test A-decl-1 Analytical Solution}
	\label{tab:test-A-decl-1ana}
	\begin{tabular}{|l|l|l|}
		\hline
		\textbf{Time Step} & \textbf{\shortstack{No. of Source \\Facilities Deployed}}& \textbf{\shortstack{No. of Source \\Facilities Decomissioned}}\\
		\hline
		1 to 12 & 1 & 0\\
		13 & 0 & 1\\
		14 to 15 & 0 & 0\\
		\hline
	\end{tabular}
\end{table}

\section{Numerical Test Results}
It was found that none of the exact tests and base case tests passed. 
The failures are attributed to three reasons:

\begin{enumerate}
	\item There is a test failure when there is no initial facility present. An initial condition must be given for the algorithm to understand the capacity of the facility it deploys.
	\item There is a test failure when there is growth in the demand. The algorithm failed to deploy facilities to meet the increase in demand.
	\item There is a test failure when facilities are expected to be decommissioned. There is yet to be an implementation on decommissioning behavior.
\end{enumerate}

Despite failures in these situations, the non-optimizing method proved to have commissioning capabilities
to meet demand. Because of the limitation in the algorithm, it is hard to predict demand with precision
in such a short time. However, the same numerical experiments can be applied to the deterministic
optimizing algorithm, which holds more promise. The goal is that the deterministic optimization method
will be able to overcome the issues faced by the non-optimizing method with reference to the
requirement of an initial condition, growth in demand. Also, the capability to decommission facilities
upon oversupply will be added.

Appendix C reflects the numerical experiment solution output by the non-optimizing prediction algorithm for each test scenario defined in section 6. 

\pagebreak

\section{References}
\bibliography{bibliography}

\pagebreak

\section*{Appendix A - parameter configuration}
Appendix A shows the json file that contains the simulation parameters that are common between all the test scenarios discussed in Section 6.  

\begin{minted}{json}
template = {
"simulation": {
"archetypes": {
"spec": [
{"lib": "agents", "name": "NullRegion"}, 
{"lib": "cycamore", "name": "Source"}, 
{"lib": "cycamore", "name": "Reactor"},
{"lib": "cycamore", "name": "Sink"},
{"lib": "d3ploy.no_inst", "name": "NOInst"}
]
}, 
"control": {"duration": "15", "startmonth": "1", "startyear": "2000"}, 
"recipe": [
{
"basis": "mass", 
"name": "fresh_uox", 
"nuclide": [{"comp": "0.711", "id": "U235"}, {"comp": "99.289", "id": "U238"}]
}, 
{
"basis": "mass", 
"name": "spent_uox", 
"nuclide": [{"comp": "50", "id": "Kr85"}, {"comp": "50", "id": "Cs137"}]
}
], 
"facility": [{
"config": {"Source": {"outcommod": "fuel",
"outrecipe": "fresh_uox",
"throughput": "1",
"source_record_supply": "fuel"}}, 
"name": "source"
},
{
"config": {"Sink": {"in_commods": {"val":"spent_uox"},
"max_inv_size": 1,
"sink_record_demand": "fuel_cap"}}, 
"name": "sink"
},
{
"config": {
"Reactor":{
"assem_size":"1",
"cycle_time": "1", 
"fuel_incommods": {"val": "fuel"}, 
"fuel_inrecipes": {"val": "fresh_uox"}, 
"fuel_outcommods": {"val": "spent_uox"}, 
"fuel_outrecipes": {"val": "spent_uox"}, 
"n_assem_batch": "1", 
"n_assem_core": "1", 
"power_cap": "1", 
"refuel_time": "0",
"reactor_fuel_demand": "fuel_reactor"
}
},
"name": "reactor"
}]}}
\end{minted}

\pagebreak
\section*{Appendix B - Sample Test Code }
\subsection*{Sample test code for test A-const-1}
Appendix B shows the python file that contains the a segment of the simulation parameters that are unique to test A-const-1 and the code for test A-const-1. 
\begin{minted}{python}
# Test A_const_1
INIT_DEMAND = copy.deepcopy(TEMPLATE)
INIT_DEMAND["simulation"].update({"region": {
"config": {"NullRegion": "\n      "},
"institution": {
"config": {
"NOInst": {
"calc_method": "arma",
"demand_commod": "POWER",
"demand_std_dev": "0.0",
"growth_rate": "0.0",
"initial_demand": "1",
"prototypes": {"val": "source"},
"steps": "1",
"supply_commod": "fuel"
}
},
"name": "source_inst"
},
"name": "SingleRegion"
}})

@pytest.mark.base
def test_a1_init_demand():
# tests if NOInst deploys a source
# given initial demand and no initial facilities
output_file = 'init_file.sqlite'
input_file = output_file.replace('.sqlite', '.json')
with open(input_file, 'w') as f:
json.dump(INIT_DEMAND, f)
s = subprocess.check_output(['cyclus', '-o', output_file, input_file],
universal_newlines=True, env=ENV)
# check if ran successfully
assert("Cyclus run successful!" in s)

# getting the sqlite file
cur = get_cursor(output_file)

# check base solution
source_base = cur.execute(query).fetchone()
assert(1 <= source_base[0] <= (1 + tol))

@pytest.mark.exact
def test_a1_init_demand_exact():
output_file = 'init_file.sqlite'
cur = get_cursor(output_file)
# check exact solution
source_exact = cur.execute(query + " AND EnterTime = 1").fetchone()
assert(source_exact[0] == 1)
\end{minted}

\pagebreak

\section*{Appendix C - Numerical Experiment Solution for test scenarios}
\subsection*{Test A-const-1}
\begin{table}[H]
	\centering
	\caption{Test A-const-1 Numerical Experiment Solution}
	\label{tab:test-A-const-1num}
	\begin{tabular}{|l|l|}
		\hline
		\textbf{Time Step} & \textbf{\shortstack{No. of Source \\Facilities Deployed}}\\
		\hline
		1 to 15& 0\\
		\hline
	\end{tabular}
\end{table}

\subsection*{Test A-const-2}
\begin{table}[H]
	\centering
	\caption{Test A-const-2 Numerical Experiment Solution}
	\label{tab:test-A-const-2a2num}
	\begin{tabular}{|l|l|}
		\hline
		\textbf{Time Step} & \textbf{\shortstack{No. of Source \\Facilities Deployed}}\\
		\hline
		1 & 0\\
		2 & 1\\
		3 & 1\\
		4 & 1 \\
		5 & 0 \\
		6 & 1 \\
		7 to 15 & 0 \\
		\hline
	\end{tabular}
\end{table}

\subsection*{Test A-grow-1}
\begin{table}[H]
	\centering
	\caption{Test A-grow-1 Numerical Experiment Solution}
	\label{tab:test-A-grow-1num}
	\begin{tabular}{|l|l|}
		\hline
		\textbf{Time Step} & \textbf{\shortstack{No. of Source \\Facilities Deployed}}\\
		\hline
		1 to 15& 0\\
		\hline
	\end{tabular}
\end{table}

\subsection*{Test A-grow-2}
\begin{table}[H]
	\centering
	\caption{Test A-grow-2 Numerical Experiment Solution}
	\label{tab:test-A-grow-2num}
	\begin{tabular}{|l|l|}
		\hline
		\textbf{Time Step} & \textbf{\shortstack{No. of Source \\Facilities Deployed}}\\
		\hline
		1 to 15& 0\\
		\hline
	\end{tabular}
\end{table}

\subsection*{Test B-const-1}
\begin{table}[H]
	\centering
	\caption{Test B-const-1 Numerical Experiment Solution}
	\label{tab:test-B-const-1num}
	\begin{tabular}{|l|l|l|}
		\hline
		\textbf{Time Step} & \textbf{\shortstack{No. of Source \\Facilities Deployed}} & \textbf{\shortstack{No. of Reactor \\Facilities Deployed}}\\
		\hline
		1 to 15 & 0 & 0\\
		\hline
	\end{tabular}
\end{table}

\subsection*{Test B-const-2}
\begin{table}[H]
	\centering
	\caption{Test B-const-2 Numerical Experiment Solution}
	\label{tab:test-B-const-2num}
	\begin{tabular}{|l|l|l|}
		\hline
		\textbf{Time Step} & \textbf{\shortstack{No. of Source \\Facilities Deployed}} & \textbf{\shortstack{No. of Reactor \\Facilities Deployed}}\\
		\hline
		1 & 0 & 0\\
		2 & 1 & 0\\
		3 & 1 & 0\\
		4 & 1 & 0\\
		5 & 0 & 0\\
		6 & 1 & 0\\
		7 to 15 & 0 & 0\\
		\hline
	\end{tabular}
\end{table}

\subsection*{Test B-grow-1}
\begin{table}[H]
	\centering
	\caption{Test B-grow-1 Numerical Experiment Solution}
	\label{tab:test-B-grow-1num}
	\begin{tabular}{|l|l|l|}
		\hline
		\textbf{Time Step} & \textbf{\shortstack{No. of Source \\Facilities Deployed}} & \textbf{\shortstack{No. of Reactor \\Facilities Deployed}}\\
		\hline
		1 to 15 & 0 & 0\\
		\hline
	\end{tabular}
\end{table}

\subsection*{Test A-const-3}
\begin{table}[H]
	\centering
	\caption{Test A-const-3 Numerical Experiment Solution}
	\label{tab:test-A-const-3num}
	\begin{tabular}{|l|l|l|}
		\hline
		\textbf{Time Step} & \textbf{\shortstack{No. of Source \\Facilities Deployed}}& \textbf{\shortstack{No. of Source \\Facilities Decomissioned}}\\
		\hline
		1 to 15 & 0 & 0\\
		\hline
	\end{tabular}
\end{table}

\subsection*{Test A-decl-1}
\begin{table}[H]
	\centering
	\caption{Test A-decl-1 Numerical Experiment Solution}
	\label{tab:test-A-decl-1num}
	\begin{tabular}{|l|l|l|}
		\hline
		\textbf{Time Step} & \textbf{\shortstack{No. of Source \\Facilities Deployed}}& \textbf{\shortstack{No. of Source \\Facilities Decomissioned}}\\
		\hline
		1 to 15 & 0 & 0\\
		\hline
	\end{tabular}
\end{table}

\end{document}



