\documentclass[11pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{caption} % for table captions
\usepackage{amsmath} % for multi-line equations and piecewises
\DeclareMathOperator{\sign}{sign}
\usepackage{graphicx}
\usepackage{relsize}
%\usepackage{textcomp}
\usepackage{xspace}
\usepackage{verbatim} % for block comments
%\usepackage{subfig} % for subfigures
\usepackage{enumitem} % for a) b) c) lists
\newcommand{\Cyclus}{\textsc{Cyclus}\xspace}%
\newcommand{\Cycamore}{\textsc{Cycamore}\xspace}%
\usepackage{tabularx}
\usepackage{color}
\usepackage[acronym,toc]{glossaries}
\include{acros}
\definecolor{bg}{rgb}{0.95,0.95,0.95}
\newcolumntype{b}{X}
\newcolumntype{f}{>{\hsize=.15\hsize}X}
\newcolumntype{s}{>{\hsize=.5\hsize}X}
\newcolumntype{m}{>{\hsize=.75\hsize}X}
\newcolumntype{r}{>{\hsize=1.1\hsize}X}
\usepackage{titling}
\usepackage[hang,flushmargin]{footmisc}
\renewcommand*\footnoterule{}
\usepackage[newfloat]{minted}
\newenvironment{code}{\captionsetup{type=listing}}{}
\SetupFloatingEnvironment{listing}{name=Code}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}

\bibliographystyle{abbrv}
\usepackage{tikz}


\usetikzlibrary{shapes.geometric,arrows}
\tikzstyle{process} = [rectangle, rounded corners, minimum width=1cm, minimum height=1cm,text centered, draw=black, fill=blue!30]
\tikzstyle{arrow} = [thick,->,>=stealth]
\tikzstyle{cloud} = [draw, ellipse,fill=red!20, node distance=3cm,
minimum height=2em]

\graphicspath{{images/}}
\title{Numerical Experiments for Verifying Demand Driven Deployment Algorithms 
        \\ \vspace{0.5em} Deterministic-Optimizing Algorithm}
\author{Jin Whan Bae, Gwendolyn Chee, Kathryn Huff}


\begin{document}
	\maketitle
	\hrule

\section{Introduction}
For many fuel cycle simulations, it is currently up to the user to define
a deploy scheme, or facility parameters, to make sure that there's no gap
in the supply chain. Or, the same goal is achieved by setting the supply
\texttt{facility}'s capacity to infinity, which does not reflect real-world
conditions. 

The Demand-Driven Cycamore Archetype project (NEUP-FY16-10512) aims to develop demand-driven deployment capabilities
in \Cyclus. To understand the terms used in this report, please read \cite{huff_fundamental_2016}. 

The developed algorithm, in the form of \Cyclus \texttt{Institution}
agent, deploys \texttt{Facilities} to meet the front-end and back-end demands of the 
fuel cycle.

This report describes numerical experiments for the deterministic
-optimizing algorithm.

These prediction models are being developed by the University of South Carolina. The numerical experiments will be designed for both
 the once through nuclear fuel 
cycle and advanced fuel cycles. 

\section{Method}
This report lists necessary capabilities of the new \Cyclus \texttt{institute}
for demand-driven deployment of fuel cycle facilities. 
Then the report lists tests to check correct implementation of the capabilities,
with a sample fuel cycle with well-defined facility parameters.


\section{Configuration}
The user defines a demand equation of a commodity (e.g. power, spent fuel, plutonium etc.)
and a supply chain that results in the creation of the demanded commodity.
For example, a user would define a power demand equation, and list
the facilities that lead up to power production, as such:

\begin{minted}{xml}
<!-- Definition of demand commodity and demand equation -->
<demand_commodity> POWER </demand_commodity>
<piecewise_function>
	<piece>
		<start>0</start>
		<function>
			<type>linear</type>
			<params> 1 2 </params>
		</function>
	</piece>
</piecewise_function>

<!-- Definition of supply chain leading to power production -->
<supply_chain>
	<val> source </val>
	<val> enrichment </val>
	<val> reactor </val>
</supply_chain>

<!-- Added definition of supply and demand commodities -->
\end{minted}

Note that the user input is expansive and detailed due to the 
independent, agent-based nature of \Cyclus. The user-defined
parameters will allow the institution create a supply chain,
demand timeseries for each commodity, and deployment timeseries,
which will be explained in the next section.

\section{Algorithm Flow}

The algorithm is an \texttt{Institution}, which is a \Cyclus agent type
that deploys and decommissions facilities.

Upon entering, the \Cyclus \texttt{Institution} accesses the parameters for each
facility in the chain to extract the supply and demand parameters (capacity, throughput).
The algorithm then creates a matrix of commodity demand quantities for every
facility of the supply chain. It does so by first creating a vector
of the final demand (e.g. power) and back-calculating the demand for other
commodities in order to meet power production demand.
The matrix has a size of \texttt{[Timestep X Length of Chain]}.
The demand quantity matrix is then calculated into a deployment matrix that
lists the number of facilities to be deployed at a given timestep.


\subsection{Specifics}


\subsection{Time Step Execution in \Cyclus}
As a reference, the time step execution for \Cyclus is illustrated in figure \ref{diag:time}.

At \texttt{Tock}, the algorithm calculates the demand and supply for the next timestep, and calculates
the difference. If the difference is bigger than the capacity of one facility, it
schedules to deploy a new facility, or a decommissioning of an existing facility.
The decommissioning takes place in the \texttt{Decommission} phase of \Cyclus, and
the construction takes place in the \texttt{Build} phase of \Cyclus. Thus, all the
adjustment of facilities occur prior to the next \gls{DRE}.


\begin{figure}[H]
\centering
\begin{tikzpicture}[node distance=1.5cm]
\node (Build) [process] {Build (kernel)};
\node (Tick) [process, below of=Build] {Tick (agent)};
\node (DRE) [process, below of=Tick]{Dynamic Resource Exchange (kernel) };
\node (Tock) [process, below of=DRE]{Tock (agent)};
\node (Decom) [process, below of=Tock] {Decommission (kernel)};

\draw [arrow] (Build) -- (Tick); 
\draw [arrow] (Tick) -- (DRE);
\draw [arrow] (DRE) -- (Tock);
\draw [arrow] (Tock) -- (Decom);
\end{tikzpicture}
\caption{Each timestep in \Cyclus follows the five steps in order. Processes labeled
         kernel are executed by the \Cyclus framework, whereas processes labeled agent
         are executed by individual agents. What happens in the `Tick' and `Tock' is
         thus unique to each archetype.}
\label{diag:time}
\end{figure}


\section{Simulation parameter for Test Scenarios}
Simple parameters are given to fuel cycle facilities for the numerical testing of 
the algorithm.  Only \texttt{source} and \texttt{reactor} facilities are used in the test scenarios. 

Table \ref{tab:testscenario} provides basic parameters for each test scenario. Table \ref{tab:reactor} provides the parameters for the \texttt{source}, \texttt{reactors} and \texttt{sink} in the test scenarios.

\begin{table}[H]
	\centering
	\caption {Basic Test Parameters}
	\label{tab:testscenario}
	\begin{tabular}{|l|l|l|}
		\hline
		\textbf{Test Scenario Parameters} & \textbf{Value} & \textbf{Units} \\
		\hline
		Duration & 15 & timesteps \\
		Timestep & 1 & month \\
		Start Month & 1 & month \\
		Start Year & 2000 & year \\
		\hline
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
    \caption {Source, Reactor and Sink Parameters}
	\label{tab:reactor}
	\begin{tabular}{|l|l|l|}
\hline
\textbf{Source Parameters} & \textbf{Value} & \textbf{Units} \\
\hline
Throughput & 1 & kg / time step \\
Output Commodity & fuel & kg\\
Lifetime & 4 & time steps \\
% what is this wait time
Wait time & 3 & time steps \\
\hline
\textbf{Reactor Parameters} & \textbf{Value} & \textbf{Units} \\
\hline
Input Commodity & fuel & kg\\
Output Commodity & power & MWe\\
Power Capacity & 1& MWe \\
Cycle Time & 1 & time steps \\
Refuel Time & 0 & time steps \\
Lifetime & 4 & time steps \\
Assembly Size & 1 & kg \\
Num. assemblies per batch & 1 & -\\
Num. assemblies per core & 3 & - \\
\hline
	\end{tabular}
\end{table}

\pagebreak

\section{Numerical Tests for the Deterministic optimizing prediction method}
The deterministic optimizing prediction method is tested by comparing its output for various scenarios against their analytical solutions . In this section, the tests that must be met is described based on the parameters defined in table \ref{tab:testscenario} and \ref{tab:reactor} and analytical solution of a defined simple scenario. Unit test examples are included in Appendix B.

The tests are split into test A types and test B types. Test A refers to the test scenarios where there are only \texttt{source} facilities. Test B refers to the test scenarios where there are both \texttt{source} and \texttt{reactor} facilities. Each test type is sub-categorized into type 1,2 and 3. Test A1 and B1 refer to test scenarios where facilities are expected to be deployed. Tests A2 and B2 refers to the test scenarios where facilities are expected to be decommissioned. Tests A3 and B3 refers to test scenarios where facilities are expected to be deployed and decommissioned. In all scenarios the ultimate demand commodity is \texttt{Power}. Figure \ref{fig:sourceflow} and \ref{fig:sourcereactorflow} show the commodity flow for test type A and B respectively. 

\begin{figure}[H]
	\centering
	\begin{tikzpicture}[node distance=4cm]
	\node (source) [process] {\texttt{Source}};
	\node (power) [cloud, right of=source] {\texttt{Power}};
	\draw [arrow] (source) -- (power); 
	\end{tikzpicture}
	\caption{Demand flow of Test A type where only source facilities are present. Blue blocks refer to a  facility type and red ellipses refer to a commodity type.}
	\label{fig:sourceflow}
\end{figure}

\begin{figure}[H]
	\centering
	\begin{tikzpicture}[node distance=3cm]
	\node (source) [process] {\texttt{Source}};
	\node (fuel) [cloud, right of=source] {\texttt{Fuel}};
	\node (reactor) [process, right of=fuel] {\texttt{Reactor}};
	\node (power) [cloud, right of=reactor] {\texttt{Power}};	
	
	\draw [arrow] (source) -- (fuel); 
	\draw [arrow] (fuel) -- (reactor); 
	\draw [arrow] (reactor) -- (power); 
	\end{tikzpicture}
	\caption{Demand flow of Test B type where source and reactor facilities are present. Blue blocks refer to a  facility type and red ellipses refer to a commodity type.}
	\label{fig:sourcereactorflow}
\end{figure}

The tests listed below are unique to the deterministic optimizing algorithm. The tests written in the non-optimizing algorithm report will also be used to test the deterministic optimizing algorithm but are not listed in this report. 

The prediction algorithm for the deterministic optimizing method has two user-defined input parameters for the scenario and one user-defined input parameter per facility type present. The aim of the various test scenarios are to check if the deterministic optimizing method archetype will deploy or decommission facilities correctly when there is a variation in the combination of these input parameters.  \\

% This should be melted into the input parameters section
% We should deviate away from growth rate -> stepwise functions
The two scenario input parameters are: 
\begin{enumerate}
	\item Initial demand of Power
	\item Growth rate of Power demand
\end{enumerate}

The one user-defined input parameter per facility type:
\begin{enumerate}
	\item Number of initial facilities (initial supply)
\end{enumerate}

For each test scenario, there is one table that states the test scenario's input parameters and another table that states the exact analytical solution. 

Additionally, we created base tests that pass when the supply meets the demand within a given facility number tolerance. In other words, when the supply exceeds the demand by the specified tolerance quantity, the test still passes. For this numerical experiment, the tolerance is set to one facility. For example in test A-1, the expected total number facilities deployed is 1, and since the facility over-prediction tolerance is 1, the acceptable range of total number of facilities $(x)$ deployed in the entire test scenario is $1<x<2$. If the total number of facilities deployed is within this range, the base case test will pass. Note that there is no tolerance for under-supplying.   

% why does it start from a3-1?
\subsection{Test A3-1}
The goal of test A3-1 is to determine is a source facility is deployed when the lifetime of another is ending to meet the upcoming loss of power supply. 
Table \ref{tab:testa3-1} shows the input parameters of the source facility in the test scenario. Table \ref{tab:testa3-1ana} shows the expected analytical solution based on the test scenario. Table \ref{tab:testa3-1base} shows the accepted range of total number of facilities deployed and decommissioned over the test scenario which will pass the base test, which factors in the facility over or under prediction tolerance of 1. 
\begin{table}[H]
	\centering
	\caption{Test A3-1 Scenario Input Parameters }
	\label{tab:testa3-1}
	\begin{tabular}{|l|l|l|}
		\hline
		\textbf{Power} & \textbf{Value} & \textbf{Units} \\
		\hline 
		Initial demand & 1 & Mwe \\
		Growth Rate & 0 & \\
		\hline
		\textbf{Source Parameter} & \textbf{Value} & \textbf{Units} \\
		\hline
		Initial facilities & 1 & \#\\
		\hline
	\end{tabular}
\end{table}

% why?
\begin{table}[H]
	\centering
	\caption{Test A3-1 Analytical Solution (If the time step is skipped over, it is because there are no facilities deployed or decommissioned during that time step.)}
	\label{tab:testa3-1ana}
	\begin{tabular}{|l|l|l|}
		\hline
		\textbf{Time Step} & \textbf{\shortstack{No. of Source \\Facilities Deployed}} & \textbf{\shortstack{No. of Source \\Facilities Decommissioned}} \\
		\hline
		0 & 1 & 0 \\
		3 & 0 & 1 \\
		4 & 1 & 0 \\
		7 & 0 & 1 \\
		8 & 1 & 0 \\
		11 & 0 & 1 \\
		12 & 1 & 0 \\
		15 & 0 & 1 \\
		\hline
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
	\caption{Test A3-1 Base Test Acceptance}
	\label{tab:testa3-1base}
	\begin{tabular}{|P{7.5cm}|}
		\hline
		\textbf{\shortstack{Acceptable total No. of Source \\Facilities Deployed + tolerance}}\\
		\hline
		3 $<$ x $<$ 4 \\
		\hline
		\textbf{\shortstack{Acceptable total No. of Source \\Facilities Decommisioned - tolerance}}\\
		\hline
		3 $<$ x $<$ 4 \\
		\hline
	\end{tabular}
\end{table}

\subsection{Test A3-2}
% wording
The goal of test A3-2 is to determine whether a source facility is deployed when the lifetime of another is ending to meet the upcoming loss of power supply when there multiple source facilities decommissioning and deploying at different times. 
Table \ref{tab:testa3-2} shows the input parameters of the source facility in the test scenario. Table \ref{tab:testa3-2ana} shows the expected analytical solution based on the test scenario. Table \ref{tab:testa3-2base} shows the accepted range of total number of facilities deployed and decommissioned over the test scenario which will pass the base test, which factors in the facility over or under prediction tolerance of 1. 
\begin{table}[H]
	\centering
	\caption{Test A3-2 Scenario Input Parameters }
	\label{tab:testa3-1}
	\begin{tabular}{|l|l|l|}
		\hline
		\textbf{Power} & \textbf{Value} & \textbf{Units} \\
		\hline 
		Initial demand & 2 & Mwe \\
		Growth Rate & 0 & \\
		\hline
		\textbf{Source Parameter} & \textbf{Value} & \textbf{Units} \\
		\hline
		Initial facilities & 1 & \#\\
		\hline
	\end{tabular}
\end{table}

% huhu?
\begin{table}[H]
	\centering
	\caption{Test A3-2 Analytical Solution (If the time step is skipped over, it is because there are no facilities deployed or decommissioned during that time step.)}
	\label{tab:testa3-2ana}
	\begin{tabular}{|l|l|l|}
		\hline
		\textbf{Time Step} & \textbf{\shortstack{No. of Source \\Facilities Deployed}} & \textbf{\shortstack{No. of Source \\Facilities Decommissioned}} \\
		\hline
		0 & 1 & 0 \\
		1 & 1 & 0 \\
		3 & 0 & 1 \\
		4 & 1 & 1 \\
		5 & 1 & 0 \\
		7 & 0 & 1 \\
		8 & 1 & 1 \\
		11 & 0 & 1 \\
		12 & 1 & 1 \\
		15 & 0 & 1 \\
		\hline
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
	\caption{Test A3-2 Base Test Acceptance}
	\label{tab:testa3-1base}
	\begin{tabular}{|P{7.5cm}|}
		\hline
		\textbf{\shortstack{Acceptable total No. of Source \\Facilities Deployed + tolerance}}\\
		\hline
		6 $<$ x $<$ 7 \\
		\hline
		\textbf{\shortstack{Acceptable total No. of Source \\Facilities Decommisioned - tolerance}}\\
		\hline
		6 $<$ x $<$ 7 \\
		\hline
	\end{tabular}
\end{table}

\subsection{Test A3-3}
The goal of test A3-3 is to determine if a source facility is not decommissioned until after the wait time (defined in Table \ref{tab:reactor}) even if there is over-supply of power commodity. 
Table \ref{tab:testa3-3} shows the input parameters of the source facility in the test scenario. Table \ref{tab:testa3-3ana} shows the expected analytical solution based on the test scenario. Table \ref{tab:testa3-3base} shows the accepted range of total number of facilities deployed and decommissioned over the test scenario which will pass the base test, which factors in the facility over or under prediction tolerance of 1. 
\begin{table}[H]
	\centering
	\caption{Test A3-3 Scenario Input Parameters }
	\label{tab:testa3-3}
	\begin{tabular}{|l|l|l|}
		\hline
		\textbf{Power} & \textbf{Value} & \textbf{Units} \\
		\hline 
		Initial demand & 1 & Mwe \\
		Growth Rate & 0 & \\
		\hline
		\textbf{Source Parameter} & \textbf{Value} & \textbf{Units} \\
		\hline
		Initial facilities & 2 & \#\\
		\hline
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
	\caption{Test A3-3 Analytical Solution (If the time step is skipped over, it is because there are no facilities deployed or decommissioned during that time step.)}
	\label{tab:testa3-3ana}
	\begin{tabular}{|l|l|l|}
		\hline
		\textbf{Time Step} & \textbf{\shortstack{No. of Source \\Facilities Deployed}} & \textbf{\shortstack{No. of Source \\Facilities Decommissioned}} \\
		\hline
		0 & 1 & 0 \\
		3 & 0 & 1 \\
		\hline
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
	\caption{Test A3-3 Base Test Acceptance}
	\label{tab:testa3-3base}
	\begin{tabular}{|P{7.5cm}|}
		\hline
		\textbf{\shortstack{Acceptable total No. of Source \\Facilities Deployed + tolerance}}\\
		\hline
		1 $<$ x $<$ 2 \\
		\hline
		\textbf{\shortstack{Acceptable total No. of Source \\Facilities Decommisioned - tolerance}}\\
		\hline
		0 $<$ x $<$ 1 \\
		\hline
	\end{tabular}
\end{table}

\subsection{Test B1-1}
The goal of test B1-1 is to determine if source and reactor facilities are deployed when the lifetime of another is ending. 
Table \ref{tab:testb1-1} shows the input parameters of the source facility in the test scenario. Table \ref{tab:testb1-1ana} shows the expected analytical solution based on the test scenario. Table \ref{tab:testb1-1base} shows the accepted range of total number of facilities deployed and decommissioned over the test scenario which will pass the base test, which factors in the facility over or under prediction tolerance of 1. 

\begin{table}[H]
	\centering
	\caption{Test B1-1 Scenario Input Parameters }
	\label{tab:testb1-1}
	\begin{tabular}{|l|l|l|}
		\hline
		\textbf{Power} & \textbf{Value} & \textbf{Units} \\
		\hline 
		Initial demand & 1 & Mwe \\
		Growth Rate & 0 & \\
		\hline
		\textbf{Source Parameter} & \textbf{Value} & \textbf{Units} \\
		\hline
		Initial facilities & 0 & \#\\
		\hline
		\textbf{Reactor Parameter} & \textbf{Value} & \textbf{Units} \\
		\hline
		Initial facilities & 0 & \#\\
		\hline
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
	\caption{Test B1-1 Analytical Solution}
	\label{tab:testa5ana}
	\begin{tabular}{|l|l|l|}
		\hline
		\textbf{Time Step} & \textbf{\shortstack{No. of Source \\Facilities Deployed}} & \textbf{\shortstack{No. of Reactor \\Facilities Deployed}}\\
		\hline
		1 & 3 & 1\\
		\hline
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
	\caption{Test B1-1 Base Test Acceptance}
	\label{tab:testa5base}
	\begin{tabular}{|P{6.5cm}|P{6.5cm}|}
		\hline
		\textbf{\shortstack{Acceptable total No. of Source \\Facilities Deployed + tolerance}} &\textbf{\shortstack{Acceptable total No. of Reactor \\Facilities Deployed + tolerance}}\\
		\hline
		3 $<$ x $<$ 4 & 1 $<$ x $<$ 2\\
		\hline
	\end{tabular}
\end{table}


\section{Numerical Test Results}


\section{References}
\bibliography{bibliography}

\section*{Appendix A - parameter configuration}

\section*{Appendix B - Sample Test Code }

\section*{Appendix C - Numerical Experiment Solution for test scenarios}

\end{document}



